Genetic Algorithm Based Formula Generation for Curve Fitting in Time Series Forecasting Implemented as Mobile Distributed Computing

### 2019-08-20 Genetic-Algorithm-Based-Formula-Generation-for-Curve-Fitting-in-Time-Series-Forecasting-Implemented-as-Mobile-Distributed-Computing/presentation.tex
Almost full presentation is done.

>>>>

\subsection{Expressions Evaluation}

\begin{frame}
\frametitle{Structures and Operators}
\begin{itemize}
	\item Simple text representation of mathematical expressions
	\item Single point cut crossover
	\item Random change of mathematical operator mutation
	\item Random change of mathematical operand mutation
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Optimization Procedure}
\small
begin \\
~  t = 0; \\
~  initialize P(t); \\
~  evaluate structures in P(t); \\
~  while termination condition not satisfied do \\
~  begin \\
~~    t = t + 1; \\
~~    select\_repro C(t) from P(t-1); \\
~~    recombine and mutate structures in C(t) \\
~~    forming C'(t); \\
~~    evaluate structures in C'(t); \\
~~    select\_replace P(t) from C'(t) and P(t-1); \\
~  end \\
end \\
\end{frame}

\begin{frame}
\frametitle{Solutions Fitness}
\begin{itemize}
	\item Invalid formulas are ignored
	\item Calculation of the valid formula 
	\item Fitness is the mean square of the error with the real life values
\end{itemize}
\end{frame}

\subsection{Client-Server Communication}

\begin{frame}
\frametitle{Keeping Solutions}
\begin{itemize}
	\item Best found local solutions are reported to the remote server
	\item On the remote server global population is kept
	\item When new mobile client is connected subset of the global population is sent as new local population
\end{itemize}
\end{frame}
